A survey of HTTP caching options on the open Semantic Web

### 2015-01-16 sanity/paper1.tex
Martin todos
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@998 43ef1190-90fd-4dd7-a769-d0121f02b80e

Caching, as defined in RFC7234, requires that the server declares how
long into the future it expects the information resource in the
response to remain fresh, i.e. how long it is permissible to use
it. Based on this, the client doesn't need to contact the server at
all to reuse a cached response, but this requires a commitment from
the content provider. The standard also gives the client an
opportunity to heuristically determine a time to live. RFC7232, on the
other hand, defines a protocol for asking the server if the cached
response is still fresh using conditional requests. This doesn't
burden the content provider with the task of estimating the time to
live beforehand, but then, it must be able to answer if the resource
has changed less expensively than serving the entire response. These
two approaches can be combined, as a client may ask if a response is
fresh after it has expired. A number of headers are relevant to the
problem, we recorded those in Table~\ref{tab:headers} in
Appendix~\ref{app:fetcher} but they were not all used in this analysis.

@@

A\todo{Do I need details on how to compute the freshness lifetime?}

@@

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others. To
test this hypothesis, we create two so-called \emph{contigency
  tables} (see e.g. \cite{kn:bj}). This formalism is suited to see if the
distribution of  \httph{Server} headers are different for those implementations that
offer caching headers from those that don't. Intuitively, we expect
these distributions to be similar, ``long-tail'' distributions, i.e. a
handful of servers are used by a large number of projects, and then it
falls off rapidly, and so, some servers are used only by very
few. Likewise, it is to be expected that only a few projects have
given caching enough attention, but that they account for the majority
of the support. The question is if the presence of caching headers is
merely a matter of proportion, or if there are some that have given it
more attention, but still is in relatively little use.

@@

Since web servers may be configured to instruct clients and proxies to
cache errors differently from successfully served requests, we should
first investigate whether we can simply use all cache headers in the
analysis, or if we should remove unsuccessful responses to avoid
introducing bias to the analysis of valid responses.

@@

In Figure~\ref{fig:hardtable}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. First, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001. We also note that it is often
prohibited to cache dataset descriptions. This is odd, since
statistics about datasets is usually costly to compute and should be
cached. The VoID specification \cite{voidnote} also notes that the
statistics are considered estimates.

>>>>

Caching, as defined in RFC7234, requires that the server declares how
long into the future it expects the information resource in the
response to remain fresh, i.e. how long it is permissible to use
it. Based on this, the client doesn't need to contact the server at
all to reuse a cached response, but this requires a commitment from
the content provider. The standard also gives the client an
opportunity to heuristically determine a time to live. RFC7232, on the
other hand, defines a protocol for asking the server if the cached
response is still fresh using conditional requests. This doesn't
burden the content provider with the task of estimating the time to
live beforehand, but then, it must be able to answer if the resource
has changed less expensively than serving the entire response. These
two approaches can be combined, as a client may ask if a response is
fresh after it has expired. A number of headers are relevant to the
problem, we recorded those in Table~\ref{tab:headers} in
Appendix~\ref{app:fetcher} but they were not all used in this
analysis.\todo{Structured walkthrough}

@@

@@

For a more systematic approach\todo{Move most to appendix}, we wish to test the hypothesis that
some servers are better configured to support caching than others. To
test this hypothesis, we create two so-called \emph{contigency
  tables} (see e.g. \cite{kn:bj}). This formalism is suited to see if the
distribution of  \httph{Server} headers are different for those implementations that
offer caching headers from those that don't. Intuitively, we expect
these distributions to be similar, ``long-tail'' distributions, i.e. a
handful of servers are used by a large number of projects, and then it
falls off rapidly, and so, some servers are used only by very
few. Likewise, it is to be expected that only a few projects have
given caching enough attention, but that they account for the majority
of the support. The question is if the presence of caching headers is
merely a matter of proportion, or if there are some that have given it
more attention, but still is in relatively little use.

@@

Since web servers may be configured to instruct clients and proxies to
cache errors differently\todo{cut most to just state stuff} from
successfully served requests, we should first investigate whether we
can simply use all cache headers in the analysis, or if we should
remove unsuccessful responses to avoid introducing bias to the
analysis of valid responses.

@@

In Figure~\ref{fig:hardtable}\todo{look for others or explain, colors}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. First, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001. We also note that it is often
prohibited to cache dataset descriptions. This is odd, since
statistics about datasets is usually costly to compute and should be
cached. The VoID specification \cite{voidnote} also notes that the
statistics are considered estimates.
